\chapter{Future Tasks}
This chapter provides a summary and table of the planned tasks and experiments for the duration of the work proposed.

\subsection{Overview of Tasks:}
This proposal calls for the investigation of manifold learning and dimensionality reduction methods which promote class discriminability and are simultaneously capable of addressing groundtruth imprecision.  Two approaches will be explored during this work: Weakly-Supervised  Manifold Learning and Weakly-Supervised  Metric Embedding. In both areas of investigation, label uncertainty will adhere to the constraints of Multiple Instance Learning.  Individual tasks fall under the following categories: 1.) Multiple Instance  Manifold  Learning, 2.) Multiple Instance Metric Embedding and 3.) Comparison to the literature.  General tasks and estimated dates of completion are listed in Section \ref{sec:task_table}.

\subsection{Tasks and Approximate Dates of Completion:} \label{sec:task_table}


\begin{longtable}{|p{10cm}|p{4cm}|} 
	\caption[List of Research Tasks]{List of research tasks and their corresponding estimated dates for completion.}
	\label{tab:future_tasks}\\
	\hline \multicolumn{1}{|p{10cm}|}{\textbf{Tasks}} & \multicolumn{1}{p{4cm}|}{\textbf{Approximate Date of Completion}} \\ \hline
	\endfirsthead
	\multicolumn{2}{c}%
	{{\bfseries \tablename\ \thetable{} -- continued from previous page}} \\
	\hline \multicolumn{1}{|p{10cm}|}{\textbf{Tasks}} &  \multicolumn{1}{p{4cm}|}{\textbf{Approximate Date of Completion}}
	\\
	\hline
	\endhead
	\hline \multicolumn{2}{|r|}{{Continued on next page}} \\ \hline
	\endfoot
	\hline \hline
	\endlastfoot


	\multicolumn{2}{|l|}{\textbf{Multiple Instance Manifold Learning}} \\
	\hline
	Develop discriminative MI manifold learning approach for bag and instance-level classification. 
	\begin{enumerate}
%			\setcounter{enumi}{2}
		\item Supervised Nonlinear DR method for bag-level classification \label{item:supervisedDR_bag_level}
		\begin{enumerate}
			\item Compare S-LE and SE-Isomap  with $k$-NN
			\begin{enumerate}
				\item Evaluate over a range of embedding dimensions
				\item Evaluate over varying levels of label uncertainty
				\item Compare performance on hand-crafted and CNN-based features
			\end{enumerate}
		\end{enumerate}
	
		\item Explore methods for out-of-sample embedding
		\begin{enumerate}
			\item Linear Reconstruction
			\item Neural Networks
			\item Methods that consider class information of training data
		\end{enumerate}
		
		\item Investigate methods for selecting positive instances for instance-level  embedding/classification
		\begin{enumerate}
			\item Clustering
			\item Diverse Density-based
			\item Maximum Likelihood/ KDE of negative instances
			\item Citation $k$-NN
			\item Multiple Instance Boosting
			\item MI Ranking
		\end{enumerate}
	
		\item Repeat experiments in \ref{item:supervisedDR_bag_level} for instance-level classification
	\end{enumerate} & \newline \vspace{1cm} 2020-04 \newline \vspace{5.8cm} 2020-05 \newline \vspace{3.1cm} 2020-08 \newline \vspace{6cm} 2020-10\\ 
	\hline
	\multicolumn{2}{|l|}{\textbf{Multiple Instance Metric Embedding}} \\
	\hline
	Develop discriminative MI metric embedding approach for bag and instance-level classification. 
	\begin{enumerate}
		%			\setcounter{enumi}{2}
		\item Investigate metric embedding approach with Siamese networks.
		\begin{enumerate}
			\item Contrastive loss
			\item Triplet loss
			\item Investigate architectures/ training times
		\end{enumerate}
		\item Compare performance for both loss functions
		\item Investigate methods for constructing pairs/triplets from both bags and instances 
	\end{enumerate} & \newline \vspace{1.1cm} 2021-03 \newline \vspace{3.1cm} 2021-05 \newline \vspace{0.1cm} 2021-06\\
	\hline
	\multicolumn{2}{|l|}{\textbf{Comparison to SOA}} \\
	\hline
	Compare proposed methods to state of the art.
	\begin{enumerate}
		%			\setcounter{enumi}{2}
		\item Code SOA MI dimensionality reduction methods, namely: MIDR, MidLABS, MIDA, CLFDA and MI-FEAR
		\item Compare to SOA MI dimensionality reduction methods in terms of bag-level and instance-level classification performance (with $k$-NN and SVM), optimal embedding dimensionality and computational complexity.
		\item  Investigate performance on different datasets: DSIAC, Gulfport, LFW, instance-level MIL dataset
	\end{enumerate} & \newline \vspace{0.2cm} 2021-09 \newline \vspace{1.2cm} 2021-11 \newline \vspace{2.1cm} 2022-01 \\

	\multicolumn{2}{|l|}{\textbf{Departmental Requirements}} \\
	\hline
	Status Meeting & 2021-04\\
	\hline
	Initial Dissertation Submission & 2022-02-01\\
	\hline
	Dissertation Defense & 2022-03-01\\
	\hline
	Final Dissertation Submission & 2022-03-12\\

\end{longtable}

